---
title: "Daniel Sánchez's CV"
author: Daniel Sánchez
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(fontawesome) # For icons
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1yOBU3kymAWXtOY60zPzBOmA45xm-YdYek0GDipeAVvo/edit?usp=sharing", 
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```

```{r}
if(params$pdf_mode){
  cat("View this CV online with links [here](https://github.com/dsanchezp18/automated-cv-dsp/blob/main/cv.html).")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/dsanchezp18/automated-cv-dsp/blob/main/cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------
```{r}
CV %>% print_contact_info
```

<center>

[`r fa('envelope', fill = 'black', height = '2em')`](mailto:dsanchezp998@gmail.com)
[`r fa('linkedin', fill = 'black', height = '2em')`](https://www.linkedin.com/in/dsanchezp18/)
[`r fa('github', fill = 'black', height = '2em')`](https://github.com/dsanchezp18)
[`r fa('link', fill = 'black', height = '2em')`](https://daniel-ec.netlify.app) 
[`r fa('twitter', fill = 'black', height = '2em')`](https://twitter.com/daniel_ec18)
[`r fa('book', fill = 'black', height = '2em')`](https://scholar.google.com/citations?user=Xt2yEYgAAAAJ&hl=en)
[`r fa('r', fill = 'black', height = '2em')`](https://rpubs.com/dsanchezp998)

<center>

Languages
--------------------------------------------------------------------------------

**Spanish**: Native

**English**: Advanced, TOEFL iBT 119/120

**French**: Basic

Skills {#skills}
--------------------------------------------------------------------------------

I have many skills.

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R packages [**datadrivencv**](https://github.com/nstrayer/datadrivencv) and [**pagedown**](https://github.com/rstudio/pagedown).

The source code is available [on my GitHub profile](https://github.com/dsanchezp18/automated-cv-dsp).

Last updated on `r format(Sys.Date(), format = '%B %Y')`.

Main
================================================================================

Daniel Sánchez {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('teaching_positions')
```

Research Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions')
```

Industry Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('industry_positions')
```

Research {data-icon=books}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```

Awards {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('awards')
```

Extracurriculars {data-icon=award}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('extras')
```
